\Large Out title here

### 2012-09-14 proposal/proposal.tex
Added my student number
added student number
removed hello :), added student number
added some introduction

\title{\Large Out title here}
\author{\small Mattijs Meiboom (student number), Robin Mills (student number)\\
			\small Tijn Schouten (student number), Spyros Ioakeimidis (2144603)}
\date{\small \today}

@@

This project is about ...

>>>>

\title{\Large Out title here}
\author{\small Mattijs Meiboom (s1398342), Robin Mills (student number)\\
			\small Tijn Schouten (s1836560), Spyros Ioakeimidis (2144603)}
\date{\small \today}

@@

This project is about classifying fMRI data in order to detect the cognitive states associated with viewing different stimuli. Specifically, viewing sentences versus viewing pictures will evoke different patterns of activity in the brain. By using classifiers we will try to capture these patterns by predicting which stimuli a participant is looking at, based on the brain activity during that time.
